Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-03 wearables_survey.tex
polished off the discussion section!

\subsection{Concerns for Smartphones and Wearables}
(REDO) Mention Adrienne's work here, and other relevant smartphone studies of any sort. I will talk about how I model Adrienne's work in the next section, Survey, just give a nod to it here and go into it later. Since my results were that people care about privacy, security, health, and social change/social stigma, any phone studies which hint at any of those things will be good to put here. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.

@@

\subsection{User Perception}
(REDO) In this paper, we investigate one of the two important questions--what are the most relevant situations to people. We do this firstly because people are really bad at knowing the likelihood of something, especially a threat with respect to security or privacy, is going to happen (sources here). And while the most damaging situations should also be addressed, this is not yet possible since these technologies haven't been adopted and the damage hasn't happened, so we don't know yet. Additionally, since the number one concern that people had with these devices was privacy (can I say result here? I guess I already did in abstract), we need to know what people consider private, which is more nuanced and requires a user study like this survey.

@@

\subsection{Future Research Directions}
(REDO, ask David's/Serge's input for this section) Additional future work is encouraged in the area of studying privacy with respect to ubiquitous computing, since we proved it was the number one concern of the users of wearable devices. Clearly, this is a hard question which has been worked on for a long time but not yet fully addressed. Even this survey just barely touched on the various factors which can influence privacy perceptions and how upset people would be.

 Also, maybe some work with respect to security threats, and how feasible they might be, and some defenses against stopping wearables devices from getting sensitive information (like blocking text, detecting sensitive situations like the bathroom, etc.). Research which defends against false information, false positive commands, and just more safeguards against the new system for wearables, whatever that is, is also something to really look into.

 Work making sure that people are aware of what is going on, using indicators, not-too-transparent interfaces, and maybe being polite (recording rules follow social rules--think polite glass talk from Jaeyeon at MSR) are going to be valuable as wearables get more sophisticated but also more adopted by people. Think about it--put people in control of the technology, not technology shifting the social norms (our survey says that one of the top concerns of people were about how wearables will change social norms).

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearable devices and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen}\cite{WearableStatNews}, so our study is reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables. However, that will also have its own bias and limitations as well, since they would not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

@@

The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics. For this reason, people were heavily primed for the open-ended question. However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index. The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.

(REDO, Should I even say this?) I messed up that motorcycle question. I wish I actually had a calibration point for high risk high benefit for the Fischoff technology assessment questions. But well, none of the new technologies fit that description so we didn't really need it critically.

@@

BENEFIT prompt:

>>>>

\subsection{Smartphones and Wearables Concerns}
(REDO) Mention Adrienne's work here, and other relevant smartphone studies of any sort. I will talk about how I model Adrienne's work in the next section, Survey, just give a nod to it here and go into it later. Since my results were that people care about privacy, security, health, and social change/social stigma, any phone studies which hint at any of those things will be good to put here. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.

@@

\subsection{Risk Perception}
(REDO) In this paper, we investigate one of the two important questions--what are the most relevant situations to people. We do this firstly because people are really bad at knowing the likelihood of something, especially a threat with respect to security or privacy, is going to happen (sources here). And while the most damaging situations should also be addressed, this is not yet possible since these technologies haven't been adopted and the damage hasn't happened, so we don't know yet. Additionally, since the number one concern that people had with these devices was privacy (can I say result here? I guess I already did in abstract), we need to know what people consider private, which is more nuanced and requires a user study like this survey.

@@

\subsection{Future Research Directions}

Our survey shows that photos, videos, and textual information is generally considered to be very sensitive. Various systems which can detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous. We also show that users are significantly more willing to offer certain data if it will only be shared with the application; and additionally, that users consider privacy as their number-one concern. Research in effective sandboxing and other software protections, effective notifications, and usable indicators are encouraged at this time. Lastly, exploratory research investigating user-reported concerns, are relevant--especially the social impact of wearable devices, measurement of inaccuracy of sensor readings presented by wearables, and rate of accidental information sharing.

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, so our study is reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables. However, that will also have its own bias and limitations as well, since they would not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

@@

%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics. For this reason, people were heavily primed for the open-ended question. However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index. The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.

%(REDO, Should I even say this?) I messed up that motorcycle question. I wish I actually had a calibration point for high risk high benefit for the Fischoff technology assessment questions. But well, none of the new technologies fit that description so we didn't really need it critically.

@@

Benefit prompt:
